### 2023-04-14 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentacao

\section{Droplet Formation}
\label{sec:drop_formation}

In the Aerosol reasearch community there is a branch of studies about droplets formation. In the droplet field a very functional for applications is the atomization, which refers to breaking the liquid in small droplets.
There is many ways of atomizing a liquid. Some using mechanical energy such as ultrassound, rotating disk\cite{Disk_atomization}, pressure or blowing air on the meniscus. But also, some of them using electric forces such as electrospray atomization.

For

@@

The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows the 3 spraying dynamics that we are most intersted in this project.

@@

Through the various classifications defined we are going to work aggregating some of them and separating beetween 5 modes as shown above:

@@

In Dripping mode the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.

@@

@@

>>>>

@@

The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows 3 spraying dynamics that we are most interesting in this project.

@@

Through the various classifications and subclassifications of spraying defined in literature we are going to aggregate some of them and separate beetween 5 modes as shown above in order of growing electric potential:

@@

Dripping mode happens when the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.

\begin{figure}[H]
  \center
  \includegraphics[width=3cm]{Figuras/19:03/drip_example.png}
  \label{fig:drip_example}
  \caption{Dripping}
\end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/19:03/intermittent_example.png}
      \label{fig:intermittent_example}
      \caption{Intermittent}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/19:03/intermittent2_example.png}
      \label{fig:intermittent2_example}
      \caption{Intermittent}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/19:03/microdripping_example.png}
      \label{fig:microdripping_example}
      \caption{Microdripping}
  \end{figure}

@@

Taylor (1964) was the first to demonstrate that electrostatic pressure and capillary pressure can be balanced at any point on the surface of a liquid cone.
